%-------------------------
% Resume in Latex
% Author : Aysha M.Machingara
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aysha M. Machingara} \\ \vspace{1pt}
    \small 412-708-8419 $|$ \small Chicago, USA $|$ \href{mailto:x@x.com}{\underline{ayshamdm@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ayshamdm}{\underline{LinkedIn}} $|$
    \href{https://github.com/ayshamdmgit}{\underline{Github}} $|$
    \href{https://quora.com/profile/Aysha-M-Machingara}{\underline{Quora}}
\end{center}



% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IBM}{Sep. 2019 -- Present}
      {Data Scientist}{Financial Services Chicago, IL/ NYC, NY}
      \resumeItemListStart
        \resumeItem{\textbf{COVID Recovery Index:} Developed COVID impact planning strategy for fortune 50 automobile insurer in the US by predicting the impact of COVID on driving at a county level with a MAPE of 10\% for 500 large US counties. Used ping data from cellphones and other socio-economic and epidemiological variables. Predicted the Unemployment rate using google trends on unemployments claims with 15\% MAPE for 35 states. Formulated metrics and built a real-time dashboard for consumption by over 100 members and presented insights to CTO}
        
        {\textit{Technology Used}: Python, pyspark, fbProphet, scikit, Tableau Server(TabPy)}
        
        \resumeItem{\textbf{Advanced Automation Platform:} Built an enterprise-ready micro-service, event-driven architecture on AWS for intelligent automation of claim handling and deployed in production, reducing manual work by 42k hours/year for fortune 50 automobile insurer in the US }
        
        {\textit{Technology Used}: Python, SQL, sqlalchemy, Terraform, CI/CD - Gitops, AWS - lambda, SQS, DynamoDB, Secrets Manager, S3, Step Functions}
        
        \resumeItem{\textbf{Natural Language Processing:} Deployed NLP framework for analyzing regulatory compliance documents and identified gaps with existing controls as REST API for real-time prediction, delivering \$12MM cost savings/year}
        
        {\textit{Technology Used}: Python, Flask, Logistic Regression, Random Forest, Gaussian MM, Latent Dirichlet Allocation, scikit-learn, spaCy (Entity Recognition) }
      \resumeItemListEnd

    \resumeSubheading
      {Affine Analytics}{Feb. 2016 -- Jul. 2018}
      {Senior Data Scientist, Managing Consultant}{Bangalore, India}
      \resumeItemListStart
       \resumeItem{\textbf{Search Experience:} Implemented Statistical, hypothesis, and A/B testing for a leading search engine in Ads Display, improving Revenue/Page by 0.5-1\%. Analyzed experiment sensitivity and implementation practicality. Formulated metrics to measure usability and total impact. Scripted optimized SQL queries to handle 500GB of data a day by analyzing Query Plans and pulled information from over 20 data sources to study user search behavior. Collaborated with stakeholders for influencing product decisions}
        
        {\textit{Technology Used}: Python, PowerBI, Excel, Microsoft Cosmos BigData(SQL), PowerPoint}
        
        \resumeItem{\textbf{Proof of Concept Solutioning:} Collaborated cross-function with leadership, product, engineering, and sales to develop Proof of Concepts by identifying trends in Retail and Tech Domain. Converted two fortune 500 clients adding revenue of \$1.5 MM}
        
        {\textit{Technology Used}: Python, Azure, PowerPoint, draw.io, Tableau}
      
        \resumeItem{\textbf{Market Mix Optimization:} Developed a non-linear multiplicative model to optimize the marketing budget for a leading fitness tracker by handling over 10 data sources, increasing ROI by 8.3\%. Built a scenario optimizer for budget planning}
        
        {\textit{Technology Used}: Python, Excel Solver}
        
        \resumeItem{\textbf{Retail Pricing Optimization:} Deployed ML model for optimizing clearance markdown using Price Elasticity and spearheaded adoption across 400\+ retail stores improving revenue by 7-9\%}
        
        {\textit{Technology Used}: Python, pyspark, Teradata (SQL), Scipy Optimization}

    \resumeItemListEnd

    \resumeSubheading
      {Mu Sigma}{Jan. 2013 -- May 2014}
      {Trainee Decision Scientist}{Bangalore, India}
      \resumeItemListStart
       \resumeItem{\textbf{Retail Pricing Strategy:} Generated \$30 MM across 1500+ stores for a leading fortune 100 retailer. Formulated metrics and performed clustering to identify price increment opportunities using national average, competitor presence, and customer price sensitivity. Built real-time dashboards to monitor and report impact to CEO}
        
        {\textit{Technology Used}:  Python, SQL, Hadoop, K-means, Tableau Server}
        
         \resumeItem{\textbf{Dashboard Automation Workflow:} Identified automation opportunities using in-house workflow and NLP for product description similarity, reducing manual intervention by 65\% (\$ 1MM savings/year). Delivered impact to C-executives in QBR}
        
        {\textit{Technology Used}: Python, SQL, NLP(TF-IDF, Cosine Similarity), Tableau Server}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Pittsburgh, PA}
      {Master of Information Systems Management; GPA: 3.79}{Aug. 2018 -- Aug. 2019}
    \resumeSubheading
      {Visvesvaraya Technological University}{Bangalore, India}
      {Bachelor of Industrial Engineering and Management; GPA: 3.90}{Sep. 2010 -- May 2014}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
\resumeItemListStart
    \resumeItem{\textbf{Idea Award at IBM:} Most Impact on Society and the World for Financial Services through Analytics}
    
    \resumeItem{\textbf{Most Innovative Award at CMU:} Code4Pennsylvania Hackathon on Opioid crisis}

    \resumeItem{\textbf{Most Practical and Innovative Award from Flipkart:} International Gridlock Hackathon on using advanced analytics to ease city traffic}
  \resumeItemListEnd
  
%-----------ENTREPRENEURSHIP-----------
\section{Entrepreneurship}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Owl\'s Nest}{Jul. 2014 -- Sep. 2015}
      {CoFounder}{Bangalore, India}
      \resumeItemListStart
       \resumeItem{\textbf{Midnight Food Delivery Service:} First of its kind midnight food delivery service turning \$5K in revenue in 2 months}
      \resumeItemListEnd
        \resumeSubHeadingListEnd
  
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, VBA} \\
     \textbf{Tools and Skills}{: Data Science, Machine Learning, Analytics, Data Visualization, Deep Learning, Statistics, Data Mining, Terraform, spaCy, Spark, Tableau, GIT, MS-Excel, Docker, PyCharm, Eclipse} \\
     \textbf{Statistics}{:Statistical Testing,  Hypothesis Testing, A/B Experimental Testing }\\
     \textbf{Databases}{: Postgres, AWS-DynamoDB, AWS-RDS, MySQL, SQL Server}\\
     \textbf{Cloud}{: AWS, Azure, IBM Cloud} \\
     \textbf{Visualiztions}{: Tableau, PowerBI, AWS Dashboarding}\\
    }}
 \end{itemize}
%-------------------------------------------
\end{document}
